Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-04-11 Moltres.tex
Three meaty paragraphs in introduction.

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\textfraction}{0.07}
\renewcommand{\floatpagefraction}{0.7}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage[export]{adjustbox}
\graphicspath{{./figures/}}
% hyperref usually has to go last
\usepackage[hidelinks]{hyperref}
% but glossaries behaves best if after hyperref
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
% cleveref only behaves if after hyperref & glossaries
\usepackage{cleveref}

@@

>>>>

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\textfraction}{0.07}
\renewcommand{\floatpagefraction}{0.7}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage[export]{adjustbox}
\graphicspath{{./figures/}}
% hyperref usually has to go last
\usepackage[hidelinks]{hyperref}
% but glossaries behaves best if after hyperref
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
% cleveref only behaves if after hyperref & glossaries
\usepackage{cleveref}
\usepackage{minted}

@@

\section{Introduction}

Molten salt reactors are a reactor concept that received considerable interest
in the 1950s and 60s with development of the Aircraft Reactor Experiment and
later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} in the
Generation-IV reactor designs, the reactor concept has gained renewed research
interest in the past decade. Some of the advantages offered by the \gls{MSR}
include lower fissile inventories, no radiation damage constraint on attainable
fuel burn-up, no spent nuclear fuel, no requirement to fabricate and handle
solid fuel, and a homogeneous isotopic composition of fuel in the
reactor. \cite{noauthor_gen_2008} These characteristics give the \gls{MSR} a
potentially unique capability for actinide burning and extension of fuel
resources.

\gls{MSR} modeling efforts are focused on description of steady-state and
transient behavior. Krepel et. al. extended the in-house light-water reactor
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR. \cite{krepel_dyn3d-msr_2007} DYN3D-MSR was compared against
experimental \gls{MSRE} data and was then used to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze the normal
operational state of the \gls{MSRE} and some channel-blocking-incident
transients. \cite{kophazi_development_2009} Additions in the Kophazi model
included entrance effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics. \cite{cammi_multi-physics_2011} Advances in this work included
solution of the fuel salt velocity field, use of heterogeneous group constants
in fuel and moderator regions, and employment of a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.

This work does not introduce new science relative to the current literature so
much as it introduces a new open tool, Moltres
\cite{lindsayad_arfc/moltres_nodate}, for \gls{MSR} simulation. Moltres is an
open source code licensed under LGPL2 terms that aims to be a tool that can be
freely used, studied, critiqued, and developed by the \gls{MSR}
community. Though Moltres is devoted to an accurate description of \gls{MSR}
physics, its openness is its defining characteristic and one that actually
promotes the former quality through transparency and easy peer review. In the
era of github and global development, open and modern software practices must be
employed in order for nuclear engineering simulation capability to keep pace
with that of fields like astronomy whose multitude of open simulation tools
(Enzo, Gadget, Flash, Gizmo, Ramses, Mesa) allows them to be the darlings of
scientific visualization and documentaries. In that vein Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to allow easy
class extensibility and minimal code duplication. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another LGPL
code that itself leans on LibMesh \cite{kirk2006libmesh}, a LGPL finite element
library, and PetSc \cite{petsc-user-ref}, a BSD toolkit for solving nonlinear
equations stemming from discretization of PDEs. MOOSE and LibMesh handle
translation of application (Moltres) defined weak PDE forms into residual and
Jacobian functions that are the inputs into PetSc Newton-Raphson solution
routines. All codes use MPI for parallel communication and are easily deployed
on massively-parallel cluster-computing platforms. MOOSE applications by default
use monolithic and implicit methods that are ideal for closely-coupled and
multi-scale physics. These methods are ideal for the model problem described in
this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it more
extensible to future problems.
